Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-08-07 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Minor sanity fix

# Add in RIN^2 values
COVARIATES$RIN2 = COVARIATES$RIN^2
ContCovariates = c(ContCovariates, 'RIN2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=8}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
tmp = COVARIATES.CORRELATION$ESTIMATE
tmp[COVARIATES.CORRELATION$PVAL > 0.05] = 0
h = Heatmap(tmp, col = colorRamp2(c(-1,0,1), c('blue','white','red')), name = 'AssocEstimate')
draw(h, heatmap_legend_side = 'left')
```

>>>>

# Add in RIN^2 values
COVARIATES$RIN2 = COVARIATES$RIN^2
ContCovariates = c(ContCovariates, 'RIN2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=15, fig.height=15}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
tmp = COVARIATES.CORRELATION$ESTIMATE
tmp[COVARIATES.CORRELATION$PVAL > 0.05] = 0
h = Heatmap(tmp, col = colorRamp2(c(-1,0,1), c('blue','white','red')), name = 'AssocEstimate')
draw(h, heatmap_legend_side = 'left')
```
